%The first section of the RAD is an Introduction. Its purpose is to provide a brief overview of the function of the system and the reasons for its development, its scope, and references to the development context (e.g., reference to the problem statement written by the client, references to existing systems, feasibility studies). The introduction also includes the objectives and success criteria of the project. [OOSE p. 151]

\section{Purpose of the System}
\label{sec:purpose}
To create a support tool for researchers in order to perform SLR and SMS. 
The problems with manually creating SLR and SMS, is that they are time consuming, highly susceptible to errors and require cooperation of researchers (maybe even multiple teams).

\section{Scope of the System}
\label{sec:scope}
The scope of this project is to implement the back-end server side (Study Configuration Server) but also the UI for configuring the study (Study Configuration UI).

%\section{Non-scope of the System}
%
%will \emph{NOT} support the following features (amongst others):


\section{Objectives and Success Criteria of the System}
Has the following success criteria:

\begin{itemize}
	\item The system shall provide distributed research teams with a support tool to conduct SMS or SLR studies. 
	\item The system shall support the activities of planning the review and conducting reviews. The system shall allow for easy deployment and dissemination.
	\item The system must be a better alternative to Excel and other spreadsheet software.
	\item The system must fulfil all functional and non-functional requirements defined in the section proposed system.
\end{itemize}

\section{Definitions, acronyms and abbreviations}

\begin{itemize}
\item SLR: Systematic literature reviews
	\begin{itemize}
		\item SLR aims to precisely answer one or more focused research questions.
	\end{itemize}
\item SMS: Systematic mapping studies
	\begin{itemize}
		\item SMS aims to provide a wide overview of a research area.
	\end{itemize}
\item UI: User Interface
	\begin{itemize}
		\item UI is the space where the interaction between humans and machines occur
	\end{itemize}
\end{itemize}
